Age-related changes in plant growth and traits

### 2015-08-24 RA_figs.rmd
fixing little errors due to remake

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
words.top.left.logxy(mod)
legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")

@@

legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
plot(asin(sqrt(RA))~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
mod <- lm(log(growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
words.top.right.logx(mod)
legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=0.8,bty="n")

@@

* Orthoganal to these in WD vs. maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size

@@

```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
SummaryIndPCA <- SummaryInd %>%
  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
  select(prop_maxH,height,maxH,wood_density,LMA_mean,seed_size,growth_leaf,
         growth_stem_diameter,leaf_area,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight,
         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,scaled_growth_stem_diameter)

@@

plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC1_scale_mean
se1 <- PCA_by_species$PC1_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC1_scale_mean
se1 <- PCA_by_age$PC1_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC2_scale_mean
se1 <- PCA_by_species$PC2_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC2_scale_mean
se1 <- PCA_by_age$PC2_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

####PCA axis 3 again divides mainly by species
* it explains 9% of the variance (total variance explained now at 68%)  
* It is dividing the three (of 4) canopy species, HATE, PEPU, PELA, (BAER) versus
* top variable loadings: scaled_growth_stem_diameter, wood_density,growth_stem_diameter, shoot_leaf_count vs. maxH, LMA_mean, seed_size, RA  
* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diameter with wood_density

@@

mean1 <- PCA_by_species$PC3_scale_mean
se1 <- PCA_by_species$PC3_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC3_scale_mean
se1 <- PCA_by_age$PC3_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

####PCA axis 4  
* it explains 7% of the variance (total variance explained now at 74%)
* it divides stem vs shoot growth variables  
* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_growth_leaf_area, wood_density, prop_maxH, seed_size  
* BAER, EPMI, HATE and HEPU have higher values vs. BOLE, GRBU, GRSP with lower values; in a sense these later species have more shoot growth than stem growth and spend more of their life close to their maxH - which is true  
* there is no significant age component  
```{r, echo=FALSE,message=FALSE,fig.width=20, fig.height=14}
par(mfrow=c(2,3), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))

plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.15))
arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC4_scale_mean
se1 <- PCA_by_species$PC4_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC4_scale_mean
se1 <- PCA_by_age$PC4_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

>>>>

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
words.top.left.logxy(mod)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")

@@

legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
plot(asin(sqrt(RA))~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
mod <- lm(log(growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
words.top.right.logx(mod)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=0.8,bty="n")

@@

* Orthoganal to these in WD vs. maxH, LMA, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size

@@

```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
SummaryIndPCA <- SummaryInd %>%
  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
  select(prop_maxH,height,maxH,wood_density,LMA,seed_size,growth_leaf,
         growth_stem_diameter,leaf_area,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight,
         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,scaled_growth_stem_diameter)

@@

plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC1_scale
se1 <- PCA_by_species$PC1_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC1_scale
se1 <- PCA_by_age$PC1_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)
```

@@

mean1 <- PCA_by_species$PC2_scale
se1 <- PCA_by_species$PC2_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC2_scale
se1 <- PCA_by_age$PC2_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

####PCA axis 3 again divides mainly by species
* it explains 9% of the variance (total variance explained now at 68%)  
* It is dividing the three (of 4) canopy species, HATE, PEPU, PELA, (BAER) versus
* top variable loadings: scaled_growth_stem_diameter, wood_density,growth_stem_diameter, shoot_leaf_count vs. maxH, LMA, seed_size, RA  
* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diameter with wood_density

@@

mean1 <- PCA_by_species$PC3_scale
se1 <- PCA_by_species$PC3_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC3_scale
se1 <- PCA_by_age$PC3_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

####PCA axis 4  
* it explains 7% of the variance (total variance explained now at 74%)
* it divides stem vs shoot growth variables  
* high loadings for growth_stem_area, growth_leaf, LMA, seed_set vs low loadings for shoot_growth_leaf_area, wood_density, prop_maxH, seed_size  
* BAER, EPMI, HATE and HEPU have higher values vs. BOLE, GRBU, GRSP with lower values; in a sense these later species have more shoot growth than stem growth and spend more of their life close to their maxH - which is true  
* there is no significant age component  
```{r, echo=FALSE,message=FALSE,fig.width=20, fig.height=14}
par(mfrow=c(2,3), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))

plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.15))
arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC4_scale
se1 <- PCA_by_species$PC4_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
se_function(mean1,se1)

@@

mean1 <- PCA_by_age$PC4_scale
se1 <- PCA_by_age$PC4_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

### 2015-08-24 results_RAschedules_shorter.Rmd
Tidy up use of remake and functions
fixing little errors due to remake

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/functions.R")
```

@@

###Plots of size against reproductive investment
* Plots of total reproductive investment against size or height are both highly significant
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
mod <- lm(log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~total_weight, SummaryInd, log="xy",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm(log(height)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~height, SummaryInd, log="xy",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm((prop_maxH)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot((repro_inv)~(prop_maxH), SummaryInd, log="y",col=col.spp(species),pch=16,xlim=c(4e-03,1))
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(total_weight)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
plot(asin(sqrt(RA))~total_weight, SummaryInd, log="x",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

mod <- lm(log(height)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

mod <- lm((prop_maxH)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
plot((asin(sqrt(RA)))~(prop_maxH), SummaryInd,col=col.spp(species),pch=16,xlim=c(4e-03,1))
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right(mod)
```

@@

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16)
legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

@@

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(RGR~asin(sqrt(RA))*species,data=subset(SummaryInd,RA>0))
plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp(species),pch=16)
legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

@@

###Plotting RA species means against various traits
* species with higher wood density have higher RA
* taller species have lower RA
* species with higher LMA have lower RA
* no relationship between RA and seed size
* these are mean RA values across all plants, including babies and other non-reproducing individuals
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
plot(RA_mean~WD_mean,data=subset(SummarySpp,RA_mean>0), col=col.spp(species),pch=16,log="y",ylab="")
mod <- lm(WD_mean~asin(sqrt(RA_mean)),SummarySpp)
words.bottom.left.logy(mod)
plot(RA_mean~seed_size, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(seed_size)~asin(sqrt(RA_mean)), SummarySpp)
words.bottom.left.logxy(mod)
legend(.05,.28,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
plot(RA_mean~LMA_mean, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(LMA_mean)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
words.top.right.logxy(mod)
plot(RA_mean~maxH, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(maxH)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
words.bottom.left.logxy(mod)
mtext("RA",2,outer=TRUE)
```

*just plotting mean RA of mature plants is similar, although BAER throws off many plots - surprised by how high its RA is, and wondering if something is wrong with these #s
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
plot(maxH~WD_mean,data=subset(SummarySpp), col=col.spp(species),pch=16,log="y",ylab="")
mod <- lm(mature_RA_mean~asin(sqrt(mature_RA_mean)),data=subset(SummarySpp,species!="BAER"))
words.bottom.left.logy(mod)
plot(mature_RA_mean~seed_size, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(seed_size)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
words.bottom.left.logxy(mod)
legend(.05,.28,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
plot(mature_RA_mean~LMA_mean, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(LMA_mean)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
words.top.right.logxy(mod)
plot(mature_RA_mean~maxH, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(maxH)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
words.bottom.left.logxy(mod)
mtext("RA (mature plants only)",2,outer=TRUE)
```

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
mod <- lm(log(growth_stem_diameter) ~ age*WD_mean*LMA_mean*maxH*RA, SummaryInd)
anova(mod)

@@

par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1,1,.6,0.2))
plot(RA~WD_mean,data=subset(SummaryInd,RA>0), col=col.spp(species),pch=16,log="y",ylim=c(.0008,1))
points((RA+.001)~WD_mean,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(WD_mean~asin(sqrt(RA)),SummaryInd)
words.bottom.left.logy(mod)
plot(RA~seed_size, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~seed_size,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(log(seed_size)~asin(sqrt(RA)), SummaryInd)
words.bottom.left.logxy(mod)
plot(RA~LMA_mean, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~LMA_mean,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=sppage_zero_RA$RAcex)
mod <- lm(log(LMA_mean)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
words.top.right.logxy(mod)
plot(RA~maxH, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~maxH,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(log(maxH)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
words.bottom.left.logxy(mod)
```

>>>>

@@

###Plots of size against reproductive investment
* Plots of total reproductive investment against size or height are both highly significant
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
mod <- lm(log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~total_weight, SummaryInd, log="xy",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm(log(height)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~height, SummaryInd, log="xy",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm((prop_maxH)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot((repro_inv)~(prop_maxH), SummaryInd, log="y",col=col.spp(species),pch=16,xlim=c(4e-03,1))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(total_weight)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
plot(asin(sqrt(RA))~total_weight, SummaryInd, log="x",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

mod <- lm(log(height)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp(species),pch=16)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.top.right.logx(mod)

mod <- lm((prop_maxH)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
plot((asin(sqrt(RA)))~(prop_maxH), SummaryInd,col=col.spp(species),pch=16,xlim=c(4e-03,1))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right(mod)
```

@@

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

@@

```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(RGR~asin(sqrt(RA))*species,data=subset(SummaryInd,RA>0))
plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp(species),pch=16)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

@@

###Plotting RA species means against various traits
* species with higher wood density have higher RA
* taller species have lower RA
* species with higher LMA have lower RA
* no relationship between RA and seed size
* these are mean RA values across all plants, including babies and other non-reproducing individuals
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
plot(RA~WD,data=subset(SummarySpp[["mean"]],RA>0), col=col.spp(species),pch=16,log="y",ylab="")
mod <- lm(WD~asin(sqrt(RA)),SummarySpp[["mean"]])
words.bottom.left.logy(mod)
plot(RA~seed_size, SummarySpp[["mean"]], col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(seed_size)~asin(sqrt(RA)), SummarySpp[["mean"]])
words.bottom.left.logxy(mod)
legend(.05,.28,col=col.spp(), legend=labels.spp(), pch=16, cex=.8,bty="n")
plot(RA~LMA, SummarySpp[["mean"]], col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(LMA)~asin(sqrt(RA)), data=subset(SummarySpp[["mean"]],RA>0))
words.top.right.logxy(mod)
plot(RA~maxH, SummarySpp[["mean"]], col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(maxH)~asin(sqrt(RA)), data=subset(SummarySpp[["mean"]],RA>0))
words.bottom.left.logxy(mod)
mtext("RA",2,outer=TRUE)
```

*just plotting mean RA of mature plants is similar, although BAER throws off many plots - surprised by how high its RA is, and wondering if something is wrong with these #s
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
plot(maxH~WD,data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="y",ylab="")
mod <- lm(mature_RA~asin(sqrt(mature_RA)),data=subset(SummarySpp[["mean"]],species!="BAER"))
words.bottom.left.logy(mod)
plot(mature_RA~seed_size, data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(seed_size)~asin(sqrt(mature_RA)), data=subset(SummarySpp[["mean"]],species!="BAER"))
words.bottom.left.logxy(mod)
legend(.05,.28,col=col.spp(), legend=labels.spp(), pch=16, cex=.8,bty="n")
plot(mature_RA~LMA, data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(LMA)~asin(sqrt(mature_RA)), data=subset(SummarySpp[["mean"]],species!="BAER"))
words.top.right.logxy(mod)
plot(mature_RA~maxH, data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="xy",ylab="")
mod <- lm(log(maxH)~asin(sqrt(mature_RA)), data=subset(SummarySpp[["mean"]],species!="BAER"))
words.bottom.left.logxy(mod)
mtext("RA (mature plants only)",2,outer=TRUE)
```

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
mod <- lm(log(growth_stem_diameter) ~ age*WD*LMA*maxH*RA, SummaryInd)
anova(mod)

@@

par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1,1,.6,0.2))
plot(RA~WD,data=subset(SummaryInd,RA>0), col=col.spp(species),pch=16,log="y",ylim=c(.0008,1))
points((RA+.001)~WD,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(WD~asin(sqrt(RA)),SummaryInd)
words.bottom.left.logy(mod)
plot(RA~seed_size, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~seed_size,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(log(seed_size)~asin(sqrt(RA)), SummaryInd)
words.bottom.left.logxy(mod)
plot(RA~LMA, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~LMA,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=sppage_zero_RA$RAcex)
mod <- lm(log(LMA)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
words.top.right.logxy(mod)
plot(RA~maxH, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
points((RA+.001)~maxH,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
mod <- lm(log(maxH)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
words.bottom.left.logxy(mod)
```
